% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
\usepackage{enumitem}
\setlist{nolistsep,leftmargin=*}
\addtolength{\topmargin}{-.5in}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.75in} % increase text height to fit on 1-page 

\begin{document} 
\name{Peter F. Chinetti \\ peter@chinetti.me\\[8pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\bf  PRESENT ADDRESS\\Box 2032 \\3201 S. State St.\\Chicago, IL 60616\\(630).450.5725}
\address{\bf PERMANENT ADDRESS \\2558 Breckeridge Ct.\\Aurora, IL 60504 \\  (630).978.1952}
                                  
\begin{resume}

\section{JOB OBJECTIVE}          
    An engineering position where I am challenged to build interesting and complex things.
 
\section{EDUCATION}          
    B.S. Computer Engineering, Illinois Institute of Technology, Ongoing\\
    G.P.A. 3.3/4.0\\
   {\bf Camras Scholar}\\
        The Institute's highest undergraduate academic honor, the Camras Scholars Program challenges the top 1\% of the applicant pool to apply and interview with a faculty member for a place as a Camras Scholar. [1 of 30 in my class]\\
    {\bf Duchossois Leadership Scholar} \emph{Member of the inaugural class}\\
  The Duchossois Leadership Scholars Program is a nationally preeminent, elite scholarship program at IIT, attracting top students from across the country who have demonstrated exceptional leadership potential and academic success in their projected field. [1 of 3 in my class]
 
\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{1.3in}\= \hspace{3.6in}\= \kill % set up two tab positions
    {\bf Summer Intern} \>Goldman Sachs \emph{\small{-Unix Engineering}} \>Summer 2013\\
   \end{tabbing}\vspace{-20pt}
   \begin{itemize}
     \item Rewrote an application used to schedule automated operating system builds and automated tests of hardware and software.
     \item The project used Python and Redis
   \end{itemize}

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf International Participant}  \>Adelaide, South Australia \> May 2012\\
   \end{tabbing}\vspace{-20pt}
   \begin{itemize}
       \item Attended Engineering Leadership Conference of Engineers Australia
   \end{itemize}

   \begin{tabbing}
   \hspace{1.3in}\= \hspace{3.6in}\= \kill % set up two tab positions
    {\bf Research Intern} \>Illinois Institute of Technology\emph{\small{-Electrical Engineering Dept.}} \>Summer 2012\\
   \end{tabbing}\vspace{-20pt}
   \begin{itemize}
     \item Worked on a power engineering research team on a power system visualization. 
     \item The project required visualization of systems up to the order of 100000 nodes. As such, much of the project revolved around finding optimization to improve framerate.
     \item The project required coding in Java and C.
     \item A paper detailing this project will be published in an undergraduate research journal.
   \end{itemize}

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Research Intern} \>Fermi National Accelerator Laboratory     \>Summer 2010\\
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   \begin{itemize}
      \item Worked on an astrophysics research team to correlate modern telescope data using digital electronics with an older classification scheme using wet photography.
      \item Assisted a physicist by constructing an anemometer (wind speed meter) out of spare parts found around the laboratory.
      \item Wrote the website publishing the results of the projects.\\ http://quarknet.fnal.gov/fnal-uc/quarknet-summer-research/QNET2010/
   \end{itemize}

%   \begin{tabbing}
%   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
%   {\bf Student Worker}  \>Illinois Institute of Technology \> Current\\
%   \end{tabbing}\vspace{-20pt}
%   \begin{itemize}
%     \item Work with the department to install, maintain and upgrade physical security systems on campus.
%     \item Continuing development of a php and javascript based web app to track installed locations on campus.
%     \item Maintain computer networks and systems. 
%   \end{itemize}


\section{ENGINEERING SKILLS}          
    Electronic and Mechanical Prototyping, Technical Research, Java, Python and C Programming, Linux, Windows, Project Management, \LaTeX.
 
 
%\section{HONORS AND AWARDS}          
%    National AP Scholar [Benet Academy]\\
%    Illinois State Scholar [Benet Academy]\\
%    Dean's List
 
\section{EXTRACURRICULAR ACTIVITIES}          
    Illinois Tech Robotics Team
    \begin{itemize}
       \item Project lead of an electric diwheel robot.
       \item Member of the Executive board and fundraising chair of the team.
    \end{itemize}
\end{resume}
\end{document}
